Data preparation

### 2023-03-16 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Addressing nulls in position_category_code

>>>>

#### Step `r step_n`: `position_category_code`

```{r}
prep_01 <-
  prep_building %>% 
  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
  select(person_id) %>% 
  distinct() %>% 
  inner_join(prep_building) %>% 
  arrange(person_id,date) %>% 
  select(person_id,date,all_of(problem_variable %>% pull(variable)))

prep_01
```

```{r}
prep_02 <- 
  prep_01 %>% 
  group_by(across(all_of(problem_variable %>% pull(variable))),person_id) %>% 
  summarise(
    n = n(),
    date_first = first(date),
    date_last = last(date)
  ) %>% 
  arrange(person_id,n)

prep_02
```
